---
title: "Climate Profile for Cochise County, AZ"
sansfont: Calibri Light
output:
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r fig.width=8, fig.height=7,echo=FALSE}
library(png)
library(grid)
img <- readPNG("climPlots.png")
 grid.raster(img)
```
```{r fig.width=8, fig.height=3,echo=FALSE, fig.align="center"}
img <- readPNG("USDMplot.png")
 grid.raster(img)
```
\newpage

# Drought Indices: 1995-2015

```{r fig.width=8, fig.height=8,echo=FALSE}
img <- readPNG("spiPlots.png")
 grid.raster(img)
```
* SPI and SPEI calculated on 1915-2015 period of record. SPEI monthly water balance calculate using Hargreaves PET estimation. 


******
Data Citation: Livneh B., E.A. Rosenberg, C. Lin, B. Nijssen, V. Mishra, K.M. Andreadis, E.P. Maurer, and D.P. Lettenmaier, 2013: A Long-Term Hydrologically Based Dataset of Land Surface Fluxes and States for the Conterminous United States: Update and Extensions, Journal of Climate, 26, 9384–9392.


